Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-18 doc/manuscript/manuscript.Rmd
fix duplicated word
Add acknowledgements and contributions

@@

# Supplementary Information {-}

>>>>

## Acknowledgements {-}

The authors would like to thank Rebecca Higgens for providing valuable insights
into the historical context of the data collection and curation. Funding for
this research was provided by the North Central Soybean Research Program
(#639K623), a Layman Award (#2446), and start-up funds from the University of
Nebraska-Lincoln.

## Conflicts of Interest {-}

The authors declare no conflict of interest.

## Author Contributions {-}

<!-- Conceptualization: SEE. -->
<!-- Formal analysis: BSA SEE. -->
<!-- Funding acquisition: SEE. -->
<!-- Investigation: BSA. -->
<!-- Resources: SEE. -->
<!-- Supervision: BSA. -->
<!-- Visualization: BSA SEE. -->
<!-- Writing – original draft: BSA. -->
<!-- Writing – review & editing: SEE. -->

@@

\newpage
# Supplementary Information {-}
